Labour

### 2024-10-21 docsrc/documentation/notebooks/housing.Rmd
fixing up website to work on dev. can be expanded easily now after fixing some annoying bits like pathing.

---
title: "Housing"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

# Housing Quality

@@

```{r setup, include=FALSE}
source('sphinx_notebook_utils.R')
```

## Methods

@@

## Data

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_output("../../../data/transitions/test/housing_clm_2018_2019.rds")
```

## References

>>>>

---
title: "Housing"
output: html_document
bibliography: 
  - "`r here::here('docsrc', 'refs.bib')`"

---

```{r setup, include=FALSE}
library(here)
library(glmnet)
library(plyr)

source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
model_path <- here::here("data", "transitions", "housing_quality", "rfo", "housing_quality_RFO.rds")
model <- readRDS(model_path)

data <- read.csv(here::here("data", "final_US", "2020_US_cohort.csv"))
obs <- data$housing_quality
data$housing_quality_last <- data$housing_quality

preds <- ranger::predictions(stats::predict(model, data))
column_names <- colnames(preds)
preds <-glmnet::rmult(preds)
preds <- plyr::mapvalues(preds, from=c(1,2,3), to= column_names)
v <- "housing_quality"

```

## Housing Quality

@@

### Methods

@@

```{r housing_barchart, echo=FALSE}
discrete_barplot(obs, 'housing_quality')
```

### Data

@@

```{r housing_output, echo=FALSE}
options(width=120)
discrete_barplot2(obs, preds, "housing_quality") 
rfo_output(model)
```

### References

### 2024-10-21 docsrc/documentation/notebooks/labour.Rmd
fixing up website to work on dev. can be expanded easily now after fixing some annoying bits like pathing.

---
title: "Labour"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiling the website using the makefile.
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

```{r setup, include=FALSE}
source('sphinx_notebook_utils.R')
```

@@

```{r labour_barchart, echo=FALSE}
discrete_barplot("labour_state")
```

@@

```{r labour_output, echo=FALSE}
options(width=120)
nnet_output("../../../data/transitions/test/labour_nnet_2018_2019.rds")
nnet_confusion_matrix("../../../data/transitions/test/labour_nnet_2018_2019.rds", mode='multinom', 'factor(labour_state_next)')
```

>>>>

---
title: "Labour"
output: html_document
bibliography: 
  - "`r here::here('docsrc', 'refs.bib')`" # finally figure out how to combine these for debugging and actual 
---

```{r load_data, include=FALSE}
library(here)
source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
model_path <- here::here("data", "transitions", "S7_labour_state", "nnet", "S7_labour_state_2019_2020.rds")
model <- readRDS(model_path)

data <-  read.csv(here::here("data", "final_US", "2020_US_cohort.csv"))
obs <- data$S7_labour_state
preds <- stats::predict(model, data, type='class')
v <- "S7_labour_state"
```

@@

```{r labour_barchart, echo=FALSE}
discrete_barplot(obs)
discrete_barplot2(obs, preds, "S7_labour_state")
```

@@

```{r labour_output, echo=FALSE}
options(width=120)
#nnet_output("data/transitions/labour/nnet/labour_nnet_2018_2019.rds")
nnet_confusion_matrix(obs, preds, mode='multinom', 'S7_labour_state') # Note this is transition out of this state. 
```
